Safe and Robust Formal Synthesis of Digital Controllers\\ for Continuous Plants

### 2018-04-25 automatica/paper.tex
updating the benckmark description

Our benchmark suite consists of 18 SISO models extracted from the 
control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS};
these models are discretized with different sample times, leading to $167$ different benchmarks
to evaluate our proposal approach.

The \textit{DC motor} plant describes the velocity dynamics of a basic 
brushed direct current electrical machine. 
The \textit{automotive cruise control system} plant is used to keep constant 
the speed of an automobile, tracking a desired speed reference, 
compensating disturbances and uncertainties related to relief and terrain.
The \textit{pendulum} plant consists of a swinging point mass suspended from 
a frictionless pivot by means of a negligible mass rod, while the 
\textit{inverted pendulum} plant describes a system similar to the pendulum, but the point 
mass must be equilibrated above the pivot point, which is mounted on an 
one degree of freedom cart that moves over a track through a DC motor.

The \textit{magnetic suspension} plant corresponds to the discrete model of a 
simple eletromagnet-ball system, where a steel ball is levitated in air 
by the action of an electromagnetic force generated by an electromagnet.
The \textit{magnetic pointer} plant describes a pointer employed in analogue 
gauges and indicators, whose angular position dynamics is controlled 
by a magnetic field. 
The \textit{1/4 car suspension} plant corresponds to the model of a single 
wheel suspension system of a car, {\it i.e.}, the relative motion dynamics 
of a mass springer damp model, which connects the car to one of its wheels.

The \textit{computer tape driver} plant describes a computer storage device used to read and write 
data on magnetic tapes. The \textit{acrobot} plant corresponds to the model of a two-link 
underactuated robot manipulator, named acrobot, linearized by partial 
feedback linearization~\cite{acrobot}. 
The \textit{high-order system} plants correspond to a series of high-order control system model 
generally used as example for order reduction techniques~\cite{CHEN1979389}.
%Here, these benchmarks are used to evaluate the proposed control 
%synthesis technique under critical conditions, {\it i.e.}, with a large number of parameters 
%to be considered.

There are two \textit{continuous stirred tank reactor} models that describe the PH dynamics of a neutralization 
reaction of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and the temperature of a 
exothermic reaction~\cite{astrom2006advanced} in a continuous flow stirred-tank reactor. The \textit{bioreactor} 
benchmark is a linear model identified by least squares for the cell mass concentration controlled through dilution 
rate of a bioreactor~\cite{bioreactor}. The \textit{steam drum} benchmark describes the linear model for the 
level dynamics of a  boiler steam drum~\cite{boiler}.
The \textit{flexible beam} is a plant employed in vibration studies; the physical system consists of a flexible 
metallic structure with piezoceramic actuators and sensors.
The \textit{helicopter longitudinal motion} plant describes the dynamics of 
transitional motion with respect to a longitudinal plane and the 
rotational motion around the longitudinal axis.
The \textit{USCG cutter tampa heading angle} plant describes the heading angle 
dynamics of a Coast Guard cutter. 
The \textit{voltage regulator} plant consists of a linear model of a synchronous 
machine connected to an  infinite bus~\cite{KOKOTOVIC198023}.

The \textit{guidance control system} plant is another high-order system 
model used by Chen et al.~\cite{CHEN1979389}  to evaluate reduction 
techniques, which is used to determine the path of an autonomous vehicle movement.
The \textit{satellite attitude control system} plant describes the dynamics of a satellite attitude, 
{\it i.e.}, the orientation angles. An attitude control system must 
maintain the desired orientation of a satellite with respect to an 
inertial frame during all the excursion. 
The \textit{springer-mass damper system} plant is classic model for several mechanical 
systems dynamics. This benchmark describes a mass, which is fixed to a node by means 
of a springer and moves under the action of a input force, damping, and elastic force.

>>>>

Our benchmark suite consists of 18 SISO models extracted from the 
control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal};
these models are discretized with different sample times, leading to $167$ different benchmarks
to evaluate our proposal approach.

The \textit{acrobot} plant corresponds to the model of a two-link 
underactuated robot manipulator, named acrobot, linearized by partial 
feedback linearization~\cite{acrobot}.The \textit{antenna} benchmark 
describes the dynamics of the dynamics of the azimuth angle of an antenna 
motion system composed a gearbox, DC motor and amplifiers~\cite{gajic2008optimal}. 
The \textit{ballmaglev} plant corresponds to the discrete model of a simple 
eletromagnet-ball system, where a steel ball is levitated in air by the action 
of an electromagnetic force generated by an electromagnet~\cite{Franklin15}. 
The \textit{bioreactor} benchmark is a linear model identified by least squares 
for the cell mass concentration controlled through dilution rate of a 
bioreactor~\cite{bioreactor}.

The \textit{Chen\_ex1}, \textit{Chen\_ex2} and \textit{Chen\_ex3} benchmarks 
correspond to high-order control system discrete models generally used as 
case study for model order reduction techniques~\cite{CHEN1979389}. The benchmarks 
\textit{Cruise}~\cite{Franklin15} and \textit{CruiseHSCC}~\cite{Astrom08} are 
automotive  cruise control models. Automotive cruise control is used to keep 
constant the speed of an automobile, tracking a desired speed reference, 
compensating disturbances and uncertainties related to relief and terrain.

There are two continuous stirred tank reactor models named \textit{cstr} and 
\textit{cstrtmp} that describe the PH dynamics of a neutralization reaction 
of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
the temperature of a exothermic reaction~\cite{astrom2006advanced} in a continuous 
flow stirred-tank reactor. The \textit{DC motor} plant describes the velocity 
dynamics of a basic brushed direct current electrical machine.

The \textit{Flexbeam} benchmark is a plant employed in vibration studies; the 
physical  system consists of a flexible metallic structure with piezoceramic 
actuators and sensors. The \textit{guidance chen} benchmark is another 
high-order system model used by Chen et al.~\cite{CHEN1979389}  to evaluate 
model order reduction techniques; it corresponds to a guidance control system model,
which is used to determine the path of an autonomous vehicle movement. The 
\textit{helicopter} benchmark plant describes the dynamics of transitional motion 
with respect to a longitudinal plane and the rotational motion around the longitudinal 
axis for a coaxial helicopter.

The \textit{Invpendulum\_cartpos} and \textit{Invpendulum\_pendang} benchmarks
are models for the cart position and the pendulum angle of an inverted pendulum 
plant composed by a point mass must be equilibrated above the pivot point, which is 
mounted on an one degree of freedom cart that moves over a track through a DC motor.

The \textit{magpointer} corresponds to a magnetic pointer plant composed by a pointer 
employed in analogue gauges and indicators, whose angular position dynamics is 
controlled by a magnetic field. The \textit{magsuspension} describes the dynamic of
a magnetic car suspension system. The \textit{pendulum} plant consists of a swinging 
point mass suspended from a frictionless pivot by means of a negligible mass rod.

The \textit{Regulator} plant consists of a linear model of a synchronous electrical
machine connected to an  infinite bus~\cite{KOKOTOVIC198023}. The 
\textit{springer-mass damper system} plant is classic model for several mechanical 
systems dynamics. This benchmark describes a mass, which is fixed to a node by means 
of a springer and moves under the action of a input force, damping, and elastic force.
The \textit{steam drum} benchmark describes the linear model for the level dynamics 
of a  boiler steam drum~\cite{boiler}.

The \textit{suspension} benchmark corresponds to the model of a single wheel suspension 
system of a car, {\it i.e.}, the relative motion dynamics of a mass springer damp model, 
which connects the car to one of its wheels.  The \textit{tapedriver} benchmark
corresponds to the model of computer tape driver, \textit{i.e.}, a computer storage device 
used to read and write data on magnetic tapes.

%The \textit{USCG cutter tampa heading angle} plant describes the heading angle dynamics of a Coast 
%Guard cutter. The \textit{satellite attitude control system} plant describes the dynamics of a satellite 
%attitude, {\it i.e.}, the orientation angles. An attitude control system must maintain the desired 
%orientation of a satellite with respect to an 
%inertial frame during all the excursion.

%Here, these benchmarks are used to evaluate the proposed control 
%synthesis technique under critical conditions, {\it i.e.}, with a large number of parameters 
%to be considered.
